---
title: "Boston housing - LR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Helper packages
library(dplyr)    # for data manipulation
library(ggplot2)  # for awesome graphics

# Modeling packages
library(caret)    # for cross-validation, etc.
library(rsample)  # for sampling

# Model interpretability packages
library(vip)      # variable importance

install.packages("pdp")
```

```{r}
library(MASS)
library(ISLR)
```

## Exercises
Using the Boston housing data set from the pdp package, where the response feature is the median value of homes within a census tract (cmedv):

```{r}
summary(Boston)
```
```{r}
summary(medv)
```

```{r cars}
head(Boston)
```

## EDA

```{r pressure, echo=FALSE}
plot(medv~., Boston)
```

```{r}
pairs(~ medv + ptratio + black + lstat + dis + rm + crim, data = Boston, main = "Boston Data")
```
Pick a single feature and apply simple linear regression model.
Interpret the feature’s coefficient
What is the model’s performance? How does it compare to the KNN in the last module?

```{r}
# simple linear regression model

fit1=lm(medv~.,data=Boston)
summary(fit1)

# Interpret the feature’s coefficient
coef(fit1)

# What is the model’s performance? 
# How does it compare to the KNN in the last module?
plot(medv~.,Boston)
abline(fit1,col="blue")

scale(boston)
scale(fit1)
```

```{r}
confint(fit1)
```


```{r}
predict(fit1,data.frame(lstat=c(10,20,30)),interval="confidence")
```


```{r}
data.frame(lstat=c(10,20,30))
par(mfrow=c(2,2))
plot(fit1)
```

```{r}
fit2=lm(medv~lstat+age,data=Boston)
summary(fit2)

```

```{r}
fit3=lm(medv~.,Boston)
summary(fit3)

par(mfrow=c(2,2))
plot(fit3)
```
```{r}
fit4=update(fit3,~.-age-indus)
summary(fit4)
```
```{r}
fit6=lm(medv~lstat +I(lstat^2),Boston)
summary(fit6)

```
```{r}
attach(Boston)
par(mfrow=c(1,1))
plot(medv~lstat, Boston)
points(lstat,fitted(fit6), col="red",pch=20)
```
```{r}
fit7=lm(medv~poly(lstat,4))
plot(medv~lstat)
points(lstat,fitted(fit7),col="blue",pch=20)

```

```{r}
fit5=lm(medv~lstat*age,Boston)
summary(fit5)
```

```{r}
fit6=lm(medv~lstat+crim+rm+dis+black+chas+nox+rad+tax+ptratio+I(lstat^2)+I(rm^2))
summary(fit6)
```
```{r}
par(mfrow=c(2,2))
plot(fit6)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
