---
title: "Hitters exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Packages required
library(rsample)
library(tidyverse)
library(stats)
library(dplyr)
library(caret)
library(glmnet)
# Helper packages
library(ggplot2)  # for awesome graphics


data("Hitters")

Hitters %>%
    filter(!is.na(Salary)) %>%
    mutate(logSalary = log(Salary)) %>%
    select(-Salary) -> Hitters
```

## Using the Hitters dataset from the ISLR package (data(Hitters, package = "ISLR")):

```{r}
ISLR::Hitters
data(Hitters, package = "ISLR")

# Omit missing value:
Hitters = na.omit(Hitters)
```

## EDA


```{r}
# split data
set.seed(123)
h_split <- initial_split(Hitters, prop = 0.7)
h_train <- training(h_split)
h_test  <- testing(h_split)

X = model.matrix(Salary~., h_train)[,-1]
x_test = model.matrix(Salary~., h_test)[,-1]

y_train = h_train %>%
  select(Salary) %>%
  unlist() %>%
  as.numeric()

y_test = h_test %>%
  select(Salary) %>%
  unlist() %>%
  as.numeric()

```


## 1
Apply a ridge model with glmnet with Salary being the response variable.
What is the minimum MSE?
What is the minimum MSE within 1 standard error?
What are the lambda values for these MSEs?

```{r}
# transform y with log transformation
Y <- log(h_train$Salary)

ridge <- glmnet(
 x = X,
 y = Y,
 alpha = 0
)
plot(ridge, xvar = "lambda")
###
ridge <- cv.glmnet(
 x = X,
 y = Y,
 alpha = 0
)
plot(ridge)
# What is the minimum MSE?
min(ridge$cvm)
# What is the minimum MSE within 1 standard error?
ridge$lambda.1se
ridge$cvm[ridge$lambda == ridge$lambda.1se]
# What are the lambda values for these MSEs?
ridge$lambda.min

```
### 2
Apply a lasso model with glmnet.
What is the minimum MSE?
What is the minimum MSE within 1 standard error?
What are the lambda values for these MSEs?

```{r pressure, echo=FALSE}
lasso <- glmnet(
 x = X,
 y = Y,
 alpha = 1
)
plot(lasso, xvar = "lambda")
###
lasso <- cv.glmnet(
 x = X,
 y = Y,
 alpha = 1
)
plot(lasso)
# What is the minimum MSE?
min(lasso$cvm)
# What is the minimum MSE within 1 standard error?
lasso$cvm[lasso$lambda == lasso$lambda.1se]
# What are the lambda values for these MSEs?
lasso$lambda.min

```

## 3
Perform a grid search across alpha parameter values ranging between 0–1.
What is the optimal alpha and lambda values?
What is the MSE and RMSE for this optimal model?
How does it compare to your previous models?

```{r}
# Perform a grid search across alpha parameter values ranging between 0–1.
grid_search <- expand.grid(
  alpha = seq(0,1, by = .25),
  lambda = c(0.1, 10,  100, 1000, 10000)
)
grid_search

trControl=trainControl(method=“cv”, number=10)

# preform rsampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet",
  preProc = c("zv", "center", "scale"),
  trControl + trainControl(method = "cv", number = 10,
                           tunelength = 10))

# What is the optimal alpha and lambda values?
# What is the MSE and RMSE for this optimal model?
cv_glmnet$results %>% 
  filter(
    alpha == cv_glmnet$bestTune$alpha,
    lambda == cv_glmnet$bestTune$lambda
  )
```

```{r}
# How does it compare to your previous models?
pred <- predict(cv.glmnet, X)

# RMSE
RMSE(exp(pred), exp(Y))
```

## 4
Plot the top 10 most influential features. Do these features have positive or negative impacts on your response variable?


```{r}
ggplot(cv_glmnet, num_features = 10, geom = "point")
```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
