---
title: 'mars E #7'
output:
  pdf_document: default
  html_document: default
---
```{r}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Helper packages
library(dplyr)     # for data wrangling
library(ggplot2)   # for awesome plotting

# Modeling packages
library(earth)     # for fitting MARS models
library(caret)     # for automating the tuning process

# Model interpretability packages
library(vip)       # for variable importance
library(pdp)       # for variable relationships

(data(Hitters, package = "ISLR"))

```

## 1- Apply a MARS model with all features.

```{r}
# Apply a MARS model with all features.

mars_m <- earth(
  Salary ~ .,  
  data = h_train   
)
# Print model summary
print(mars_m)
```

## 2- How does the model performance compare to your previous models?

```{r pressure, echo=FALSE}
hyper_grid <- expand.grid(
  nprune = seq(2, 50, length.out = 10) %>% floor(),
  degree = 1:3
)

# perform resampling


model <- train(
  Salary ~ ., 
  data = h_train, 
  trControl = trainControl(method = "cv", number = 10),
  method = "earth", #<<
  tuneGrid = hyper_grid,
  metric = "RMSE")
  
  


model$bestTune
##    nprune degree
## 23     12      3
ggplot(model)


```

## 3- How many of the features are influential? Which 10 features are considered most influential?
```{r}
importance <- varImp(model, scale=FALSE)
print(importance)
plot(importance)

p1 <- vip(model, num_features = 10, geom = "point", value = "gcv") + ggtitle("GCV")
plot(p1)
```

## 4- Does your model include hinge functions? If so, explain their coefficient and plot their impact on the predicted response variable.
```{r}
summary(mars_m) %>% .$coefficients %>% head(10)

plot(mars_m, which = 1)
```


## 5- Does your model include interactions? If so, pick the interaction effect that is most influential and explain the coefficient.
```{r}
model$finalModel %>%
  coef() %>%  
  broom::tidy() %>%  
  filter(stringr::str_detect(names, "\\*"))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
